Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-11-19 rebuttal.txt

We would like to thank the reviewers & AC for their extremely detailed suggestions and comments. We would like to address the suggestions and concerns in order of importance suggested by the AC as follows: evaluation and discussion, similarity to "mash-up" makers, lack of automation, formatting and figures, and future work.

Evaluation - We think R2's comments suggest that our description of the tasks and experimental set-up were perhaps too parsimonious, and could be expanded to be made clearer.  The extra space that will be gained from condensing Table 1 (and possibly eliminating Table 3 altogether, as suggested by R2) will allow us to describe the tasks and methodology adequately, as well as to go into our task design justification with greater detail.  We believe that R2's comments also indicate a need to expand the description of how measures were taken, particularly pertaining to task performance (e.g. that the number of dimensions each participant considered was derived from an analysis of  speak-aloud dictation). Addressing the relevance of evaluation (R2), plan to connect with better descriptive text, the hypotheses (h1-3) with the goals initially set out in the introduction, and similarly, the measures taken with the hypotheses.

Distinction with "mashup-makers" - While we originally cited the Mashmaker, Vegemite and Marmite work, in the process of condensing related/background work, decided to cut these due to difference in emphasis of capability and interface metaphors/data flow.  Seeking to enable reuse of data "off of any web page", a major capability of mashup makers is unstructured data acquisition, e.g., page scraping, tabular aggregation and shaping.  DataPalette, meanwhile, starts with the observation that already structured data can be acquired directly from most, if not all major web sites and platform providers today.  Second,

Automation - We completely agree with R1 and R3 that careful introduction of automation could improve the user experience and reduce tedium, potentially helping people arrive at the view(s) and conclusions they want faster.  In fact, we tried a few approaches at automatic same-as reconciliation and visualisation view-inference (DWIM approaches) during our prototype design phase, and ran into a hurdles which essentially caused us to go back to the largely manual design for the final evaluation.

The first issue pertained to our observation that participants only sometimes wanted consolidated views of data -- depending on task (and sometimes even on a per-instance basis).  Un-aggregated views were preferred for reasons ranging from "it's simply easier to think about 'facebook data' vs 'what's in my address book'", to reasons of provenance ("Yelp is more trustworthy so I want to refer to it separately"). Thus, even if reconciliation was made partially automatic, it would need to be user-initiated, so that support for separated (un-aggregated) views was maintained.  
The second issue pertained to helping users cope with errors -- that debugging incorrectly-combined (false positives) or left-separated (false negatives) causes immediate confusion for non-programmers.  We observed this during testing even without automatic aggregation, when participants inadvertantly combined records when accidentally dragging and dropping items - they simply had no idea what they did, and later could not figure out why dissimilar data items were combined.

In summary we think that thus, intorduction of automation bears further design investigation, and will introduce these thoughts and possible workarounds in a "Future Work" section following "Study Limitations"

### 2012-12-26 rebuttal-2.txt

We would like to thank the reviewers & AC for their extremely detailed suggestions and comments. We would like to address the suggestions and concerns in order of importance suggested by the AC as follows: evaluation and discussion, similarity to "mash-up" makers, lack of automation, formatting and figures, and future work.

Evaluation - We think R2's comments suggest that our description of the tasks and experimental set-up were perhaps too parsimonious, and could be expanded to be made clearer.  The extra space that will be gained from condensing Table 1 (and possibly eliminating Table 3 altogether, as suggested by R2) will allow us to describe the tasks and methodology adequately, as well as to go into our task design justification with greater detail.  We believe that R2's comments also indicate a need to expand the description of how measures were taken, particularly pertaining to task performance (e.g. that the number of dimensions each participant considered was derived from an analysis of  speak-aloud dictation). Addressing the relevance of evaluation (R2), plan to connect with better descriptive text, the hypotheses (h1-3) the goals initially set out in the introduction, and similarly, the connection between the measures taken and the hypotheses.

Distinction with "mashup-makers" - We originally cited the Mashmaker, Vegemite and Marmite work, but in the process of condensing related/background work, decided to cut these due to difference in emphasis of capability.  Seeking to enable reuse of data "off of any web page", a heavy  emphases of this work is on data acquisition, e.g., page scraping, unstructured data manipulation and shaping.  DataPalette, meanwhile, while similar in the sense of encouraging data re-use, starts with the observation that already structured data can be acquired directly from most, if not all major web sites and platform providers today.

### 2012-12-26 rebuttal.txt

We would like to thank the reviewers & AC for their extremely detailed suggestions and comments.  In this rebuttal, we will briefly address the suggestions and concerns in order of importance (as described by the AC): evaluation, prestudy 1 sample bias, similarity to "mash-up" makers, potential for automation, and, paper formatting & figures.

Evaluation - R2's comments suggest that the description of the study design was perhaps too parsimonious, and should be made clearer. The extra space gained from condensing Table 1 (and possibly eliminating Table 3 altogether, as suggested by R2) should give us space to adequately describe the tasks and methodology, as well as to provide some design justification to the choice of tasks and format, including choice of measures. We believe R2's comments also indicate a need to clarify the ways each of the measures were taken; for example, we will clarify that the number of properties considered were measured by counting distinct properties mentioned during the think-aloud process. We can also provide a discussion of the potential limitations of such approaches (e.g., of think-aloud for task analysis, and how we think this technique may under-estimate results but may be still suitable for comparative analysis used consistently across conditions). Addressing the relevance of evaluation (R2), we would like to improve the descriptive text that connects the hypotheses (h1-3) with the goals set out in the intro, and similarly, the measures taken with the hypotheses. We will also call out the potential bias resulting from the subject selection process of PS1 (as suggested by R1) which involved 5 computer scientists - a substantially different source population than that for our main study.

Distinction with "mashup-makers" - While we intended to cite Mashmaker, Vegemite & Marmite, we omitted them due to perceived differences in emphasis & approach. First, these systems focused on unstructured data acquisition, e.g., scraping and collecting data from web pages. With DataPalette, we started with pre-structured data from APIs and feeds allowing for a focus on structured reconciliation problems instead. Second, DataPalette gets users to work directly with instances, while Vegemite, Marmite & Yahoo! Pipes required users to construct data-flows (using visual programming paradigms) or scripts (through programming by demonstration). We believe that directly working with instances is simpler and more accessible, although perhaps more limited, than these "simplified programming" approaches, because users avoid having to think about generalizing their actions using abstract operators. A direct-manipulation approach also better supports small-scale exploratory sensemaking by providing direct, immediate feedback. We will to mention these differences, & re-introduce references as suggested.

Automation - We agree w/ R1 & R3 that automation could improve DataPalette and potentially help people arrive at conclusions faster. We considered a number of approaches to automating same-as & view selection during the design process, but ran into challenges. First, testers only sometimes wanted the consolidate data from multiple places, on a seemingly task & individual basis. Un-consolidated instances were preferred sometimes for reasons of simplicity "it's easier to think about it separately", or for reasons of reputation & trust (e.g., "Yelp reviews are better so I separate them"). Thus, even if reconciliation were automatic, selectively (manually) initiating it might be important. The second, greater challenge pertained to error handling: errors in consolidation were difficult to detect. Even with our manual-only approach, discovering and correcting incorrectly-combined (false positives) or incompletely-combined instances (e.g., resulting from dragging & dropping items in the wrong place(s)) caused people to be confused. Thus we must consider ways to make this combination process more visible and understandable. In summary, re: automation, we think that there is much potential for automation, but it also  presents substantial interaction challenges we need to understand better.  We will mention these challenges in "Future work" at the end of the paper.

Formatting and figures - In order to make figures more readable (AC), we will expand to full-width the screen shot in Fig.1, and make the fonts of Fig.2 and Fig.5 larger as well. As described, we will consolidate T1 and eliminate T3 to make room for the above mentioned improvements. In its place, we will (slightly) expand the textual discussion of PS2 (originally explanatory text for T1) to focus on observations that most informed the design of the system. We will perform additional proofreading and corrections, including the minor edits suggested by R2 and R3.

In summary, we hope to provide a clearer, more readable and better justified final copy, using space gained from Tables 1 & 3, and improving the final discussion of results.

### 2012-12-26 chi2013-webbox-submitted.tex
getting ready to do final submission

\subsubsection{Efficiency: Time taken}
Participants spent an average of 8.9 minutes performing the tasks. Condition A (DP) took slightly less time ($M=8.7$min, $SD=1.79$) per trial than condition B ($M=9.0$min; $SD=1.44$).  An ANOVA test of time taken by interface condition blocking by participant did not find interface use a significant predictor of task completion time.  Although across trials, the restaurant selection task took on average slightly less time ($M=8.8$min,$SD=1.58$) than the university trials ($M=8.9$min,$SD=1.66$), the aforementioned ANOVA test found task type to not be a significant predictor.

\subsubsection{Thoroughness: Factors weighed in final choice}
The second metric was the number of factors the participant considered in making their final choice. To determine this, we asked participants to explain precisely why they made their choice, and matched their justifications to properties in the data.  This analysis revealed the interface used made a significant impact on the number of factors weighed ($F(1,19)=3.95; p<0.10$); participants in the DP condition listed an average of 5.5 choices in their decision ($SD=1.7$) versus 4 ($SD=1.73$) in the standard condition.

\subsubsection{Diversity: Data sources consulted}
The third metric we used to gauge how well the participant performed their tasks is the number of different data sources the participant consulted during the trial. In this metric, participants used an average of 88\% of data sources provided in the DP case, compared to 80\% in the standard interface, although an ANOVA test blocking on participant demonstrated that interface choice only approached significance in predicting the number of sources consulted ($F(1,19)=0.04$ $p\approx0.10$).

\subsubsection{Effort: External cognition}
Although we did not have an explicit measure of effort for this experiment (such as NASA's TLX \cite{tlx}) the use of paper notes provided an indicator of how much participants had to keep track of during the study.  We found that participants took notes less on average (25\%) with the DP interface than the standard interface (35\%), a difference which approached significance in an ANOVA blocked by participant ($F(1,19)= 8.22; p\approx0.10$).

\begin{figure}[htb]
\begin{center}
\includegraphics[width=8.5cm]{img/results}
\caption{\emph{Choice picks per participant trial} - Histogram of number of times each restaurant/university was chosen in DP interface (A condition) in blue/left bars, compared to the Excel/website (B condition) in red/to the right.}
\label{fig:chosen_results}
\end{center}
\end{figure}

\subsubsection{Candidate selection}

Since the tasks were subjective-choice, we could not evaluate the `correctness' of answers.  However, to determine whether there was a difference in variability of answers between interface conditions, we plotted their choice on a histogram for each trial, per task and dataset for both conditions, visible in Figure \ref{fig:chosen_results}.  As can be seen there is considerable variability and no discernible difference in variability between conditions.

>>>>

\subsubsection{Efficiency: Time taken}
Participants spent an average of 8.9 minutes performing the tasks. Condition A (DP) took slightly less time ($M=8.7$min, $SD=1.79$) per trial than condition B ($M=9.0$min; $SD=1.44$); however, a 2-way repeated measures ANOVA test of time taken by interface condition, blocked by participant ID, revealed that interface condition did not have a significant effect on task completion time.  This analysis also showed no significant effect of participant ID on task completion.  Comparing tasks, the restaurant selection task took on average slightly less time ($M=8.8$min,$SD=1.58$) than the university trials ($M=8.9$min,$SD=1.66$), but this difference was not significant.

\subsubsection{Thoroughness: Factors weighed in final choice}
The second metric was the number of factors the participant considered in making their final choice. To determine this, we asked participants to explain why they made their choice(s), and recorded the number of distinct data dimensions mentioned.  A 2-way ANOVA test of the effect of interface and participant ID on the number of factors mentioned revealed a significant effect; post-hoc analysis with Tukey-Scheff\'{e} adjustments indicated that participants in the DP condition mentioned significantly more factors ($M=5.5; SD=1.7$) than those in the control condition ($M=4; SD=1.73$), $F(1,19)=3.95; p<0.10$. A strong significant effect was also observed between participant ID and number of dimensions mentioned, meaning some participants mentioned significantly more factors than others ($F(19,19)=4.53; p < 0.001$).

\subsubsection{Diversity: Data sources consulted}
The third metric we used to gauge the task performance is the number of different data sources consulted during the trial; our rationale for this metric was that more informed decisions derived from more thorough consideration of available data. In this metric, participants used an average of 88\% ($SD=0.13$) of data sources provided in the DP case, compared to 80\% ($SD=0.18$) in the control condition, although an ANOVA test blocking on participant demonstrated that interface choice only approached significance ($F(1,19)=0.04$ $p < 0.15$).

\subsubsection{Effort: External cognition}
Although we did not have an explicit measure of effort for this experiment (such as NASA's TLX \cite{tlx}) the use of paper notes provided an indicator of how much information participants had to keep track of during the study.  We found that participants took notes less on average (25\%) with the DP interface than the standard interface (35\%), a difference which approached significance in a 2-way ANOVA blocked by participant ID ($F(1,19)= 8.22; p\approx0.10$).

\begin{figure}[tbp]
\begin{center}
\includegraphics[width=8.5cm]{img/results}
\caption{\emph{Choice picks per participant trial} - Histogram of number of times each restaurant/university was chosen in DP interface (A condition) in blue/left bars, compared to the Excel/website (B condition) in red/to the right.}
\label{fig:chosen_results}
\end{center}
\end{figure}

\subsubsection{Candidate selection}
Since the tasks were subjective-choice, we could not evaluate the `correctness' of answers.  However, to determine whether there was a difference in variability of answers between interface conditions, we plotted their choice on a histogram for each trial, per task and dataset for both conditions, visible in Figure \ref{fig:chosen_results}.  As can be seen there is considerable variability and no discernible difference in variability between conditions.
